An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-21 forecast/paper/paper.tex
More acks

\acknow{We thank Matthew Biggerstaff, Logan Brooks, Johannes Bracher, Michael 
  Johansson, Evan Ray, Nicholas Reich, and Roni Rosenfeld for several
  enlightening conversations about scoring and evaluation.  The research was  
  supported by gifts from Facebook, Google, McCune, and Optum; 
  Centers for Disease Control and Prevention (CDC) grant U01IP001121; the 
  Canadian Statistical Sciences Institute; National Sciences and Engineering
  Research Council of Canada (NSERC) grant RGPIN-2021-02618; and National
  Science Foundation Graduate Research Fellowship Program (NSF GRFP) award
  DGE175016.}

>>>>

\acknow{We thank Matthew Biggerstaff, Logan Brooks, Johannes Bracher, Michael 
  Johansson, Evan Ray, Nicholas Reich, and Roni Rosenfeld for several
  enlightening conversations about forecast scoring and evaluation.  
  This material is based on work supported by gifts from Facebook, Google.org,
  the Foundation, and Optum; Centers for Disease Control and Prevention (CDC)
  grant U01IP001121; the Canadian Statistical Sciences Institute; National
  Sciences and Engineering Research Council of Canada (NSERC) grant
  RGPIN-2021-02618; and National Science Foundation Graduate Research Fellowship 
  Program (NSF GRFP) award DGE1745016.}

### 2021-06-21 indicators/paper/paper.tex
More acks

\acknow{We thank TODO.
  This research was supported by Centers for Disease Control and Prevention
  (CDC) grant U01IP001121, and gifts from Facebook, Google, McCune, and
  Optum.}

>>>>

\acknow{We thank Carrie Reed, Matt Biggerstaff, Michael Johansson, Rachel
  Slayton, Velma Lopez, Jo Walker and others on the CDC COVID-19 Modeling Team;
  Hal Varian, Brett Slatkin, and others on Google's Surveys team and
  Google.org's CMU-Delphi Fellowship team; Curtiss Cobb and others on Facebook's   
  Demography and Survey Science, Data for Good and Health teams; Alex Smola and
  others at Amazon Web Services; Tim Suther and others at Change Healthcare;
  Paul Nielsen and others at Optum; and John Tamerius and others at Quidel.
  This material is based on work supported by gifts from Facebook, Google.org,
  the McCune Foundation, and Optum; Centers for Disease Control and Prevention
  (CDC) grant U01IP001121; National Science Foundation Graduate Research
  Fellowship Program (NSF GRFP) award DGE1745016; and the Center for Machine
  Learning and Health (CMLH) at Carnegie Mellon University.}
